---
title: ''
output: html_document
---



```{r}
library(dimple)
head(sales[,1:5])
```

# Chart Types

## Bar Charts

### Vertical Bar

```{r}
dimple(sales, xCategory="Month", xOrderRule="Date", yMeasure="Unit.Sales")
```

### Vertical Stacked Bar

```{r}
dimple(sales, xCategory="Month", xOrderRule="Date", yMeasure="Unit.Sales", series="Channel")
```

### Vertical 100% Bar

```{r}
dimple(sales, xCategory="Month", xOrderRule="Date", yPct="Unit.Sales", series="Channel")
```

### Vertical Grouped Bar

```{r}
dimple(sales, xCategory=c("Price.Tier", "Channel"), yMeasure="Unit.Sales")
```

### Vertical Stacked Grouped Bar

```{r}
dimple(sales, xCategory=c("Price.Tier", "Channel"), yMeasure="Unit.Sales", series="Owner", legend=TRUE)
```

### Vertical 100% Grouped Bar

```{r}
dimple(sales, xCategory=c("Price.Tier", "Channel"), yPct="Unit.Sales", series="Owner", legend=TRUE)
```

### Horizontal Bar

```{r}
dimple(sales, yCategory="Month", yOrderRule="Date", xMeasure="Unit.Sales")
```

### Horizontal Stacked Bar

```{r}
dimple(sales, yCategory="Month", yOrderRule="Date", xMeasure="Unit.Sales", series="Channel")
```

### Horizontal Stacked Bar

```{r}
dimple(sales, yCategory="Month", yOrderRule="Date", xPct="Unit.Sales", series="Channel")
```


### Block Matrix

```{r}
dimple(sales, xCategory=c("Channel", "Price.Tier"), yCategory="Owner", series="Price.Tier", legend=TRUE)
```

### Horizontal Floating Bars

```{r}
dimple(sales, xMeasure="Unit.Sales", yCategory="Month", yOrderRule="Date", series="Channel", stacked = FALSE, legend=TRUE)
```

### Floating Bars

```{r}
partial_data <-
  subset(sales, Month == "Dec-11")

dimple(partial_data, xMeasure="Price.Monthly.Change", yMeasure="Distribution.Monthly.Change", yOrderRule="Date", series=c("SKU","Channel"), stacked = FALSE, legend=TRUE)
```

## Pie Charts

### Pie Chart

```{r}
dimple(sales, pMeasure="Unit.Sales", series="Owner", legend=TRUE, chartType="pie")
```

### Pie Matrix

```{r}
dimple(sales, xCategory="Price.Tier", yCategory="Pack.Size", pMeasure="Unit.Sales", series="Owner", legend=TRUE, chartType="pie", piesRadius = 25)
```

### Scatter Pie

```{r}
partial_data <-
  subset(sales, Date == "01/12/2012")

dimple(partial_data, xMeasure="Price.Monthly.Change", yMeasure="Unit.Sales.Monthly.Change", pMeasure="Operating.Profit", series=c("Owner","Channel"), legend=TRUE, chartType="pie", piesRadius = 20)
```

## Scatter Charts

### Scatter

```{r}
partial_data <-
  subset(sales, Date == "01/12/2012")

dimple(partial_data, xMeasure="Unit.Sales", yMeasure="Operating.Profit", series=c("SKU","Channel"), legend=TRUE, chartType="bubble")
```

### Vertical Lollipop

```{r}
dimple(sales, xCategory="Month", xOrderRule = "Date", yMeasure="Unit.Sales", series="Channel", legend=TRUE, chartType="bubble")
```

## Bubble Charts

### Bubble

```{r}
partial_data <-
  subset(sales, Date == "01/12/2012")

dimple(partial_data, xMeasure="Unit.Sales.Monthly.Change", yMeasure="Price.Monthly.Change", zMeasure="Operating.Profit", series=c("SKU","Channel"), legend=TRUE, chartType="bubble")
```

### Bubble Matrix

```{r}
dimple(sales, xCategory=c("Channel","Price.Tier"), yCategory="Owner", zMeasure="Distribution", series="Price.Tier", legend=TRUE, chartType="bubble", seriesAggregate = "max", zOverrideMax = 200)
```

## Area Charts

### Area

```{r}
dimple(sales, xCategory="Month", xOrderRule = "Date", yMeasure="Unit.Sales", chartType="area")
```

### Stacked Area

```{r}
partial_data <-
  subset(sales, Owner %in% c("Aperture","Black Mesa"))

dimple(partial_data, xCategory="Month", xOrderRule = "Date", yMeasure="Unit.Sales", series="Channel", chartType="area", legend=TRUE)
```

### 100% Stacked Area

```{r}
partial_data <-
  subset(sales, Owner %in% c("Aperture","Black Mesa"))

dimple(partial_data, xCategory="Month", xOrderRule = "Date", yPct="Unit.Sales", series="Channel", chartType="area", legend=TRUE)
```

### Grouped Stacked Area

```{r}
partial_data <-
  subset(sales, Owner %in% c("Aperture","Black Mesa"))

dimple(partial_data, xCategory=c("Owner","Month"), xOrderRule = "Date", yMeasure="Unit.Sales", series="SKU", chartType="area", legend=TRUE, legendX=430, legendY=20, legendWidth=100, legendHeight=300, legendHorizontalAlign = "left", boundsX=70, boundsY=30, boundsWidth=340, boundsHeight=330, seriesLineWeight = 1, seriesBarGap = 0.05)
```

## Line Charts

### Single Line

```{r}
partial_data <-
  subset(sales, Owner %in% c("Aperture", "Black Mesa"))
  
dimple(sales, xCategory="Month", xOrderRule = "Date", yMeasure="Unit.Sales", chartType="line")
```

### Multiple Line

```{r}
partial_data <-
  subset(sales, Owner %in% c("Aperture", "Black Mesa"))
  
dimple(partial_data, xCategory="Month", xOrderRule = "Date", yMeasure="Unit.Sales", series="Channel", chartType="line")
```

### Grouped Single Line

```{r}
partial_data <-
  subset(sales, Owner %in% c("Aperture", "Black Mesa"))
  
dimple(partial_data, xCategory=c("Owner", "Month"), xGroupOrderRule = "Date", yMeasure="Unit.Sales", series="Owner", chartType="line")
```

## Ring Charts

### Ring Chart

```{r}
dimple(sales, pMeasure="Unit.Sales", series="Owner", legend=TRUE, chartType="pie", ringInnerRadius="50%")
```

### Grouped Lollipop Ring

```{r}
dimple(sales, xCategory=c("Price.Tier","Channel"), yMeasure="Unit.Sales", pMeasure="Unit.Sales", series="Pack.Size", legend=TRUE, chartType="pie", ringInnerRadius=20, ringOuterRadius=30)
```
